Spatial Reasoning and Statistical Graphics

### 2014-10-27 Paper/Draft1/TestingVisualAptitude.Rnw
Table fixes

\begin{savenotes}
\begin{table}[ht]
\centering
\begin{tabular}{rllll}
\hline
  & Card Rotation & Paper Folding & Figure Classification & Visual Search  \\\hline
ISU Students & \Sexpr{round(mean(ans.summary$card_rot), 1)} (\Sexpr{round(sd(ans.summary$card_rot), 1)}) 
             & \Sexpr{round(mean(ans.summary$folding), 1)} (\Sexpr{round(sd(ans.summary$folding), 1)})
             & \Sexpr{round(mean(ans.summary$fig_class), 1)} (\Sexpr{round(sd(ans.summary$fig_class), 1)})\footnote{ISU students took only Part I due to time constraints.}
             & \Sexpr{round(mean(ans.summary$vis_search), 1)} (\Sexpr{round(sd(ans.summary$vis_search), 1)})\\
Scaled Scores & 88.0 (\Sexpr{round(sqrt((24.6^2)*2), 1)})
              & 13.8 (4.5)
              & \Sexpr{round((120.0*294 + 114.9*323)/617/2, 1)} (\Sexpr{round(sqrt((30^2*294 + 27.8^2*323)/617)/2, 1)})\footnote{Averages calculated assuming 294 males and 323 females.}
              & N/A \\
Unscaled Scores & 44.0 (24.6)\footnote{Data from Part I only.}
                & 13.8 (4.5)
                & M:~120.0~(30.0), F:~114.9~(27.8)
                & N/A\\
{\footnotesize Population}    
              & \parbox[t]{.15\textwidth}{\footnotesize approx.\ 550 male\\ naval recruits} 
              & \parbox[t]{.15\textwidth}{\footnotesize 46 college students\\(1963~version)}
              & \parbox[t]{.3\textwidth}{\footnotesize suburban 11th \& 12th grade students\\(288-300 males, 317-329 females)}
              & N/A\\\hline
\end{tabular}

>>>>

\begin{savenotes}
\begin{table}[ht]
\centering
\begin{tabular}{rlllc}
\hline
  & Card Rotation & Paper Folding & Figure Classification & Visual Search  \\\hline
ISU Students & \Sexpr{round(mean(ans.summary$card_rot), 1)} (\Sexpr{round(sd(ans.summary$card_rot), 1)}) 
             & \Sexpr{round(mean(ans.summary$folding), 1)} (\Sexpr{round(sd(ans.summary$folding), 1)})
             & \Sexpr{sprintf("%.1f", mean(ans.summary$fig_class))} (\Sexpr{round(sd(ans.summary$fig_class), 1)})\footnote{ISU students took only Part I due to time constraints.}
             & \Sexpr{round(mean(ans.summary$vis_search), 1)} (\Sexpr{round(sd(ans.summary$vis_search), 1)})\\
Scaled Scores & 88.0 (\Sexpr{round(sqrt((24.6^2)*2), 1)})
              & 13.8 (4.5)
              & \Sexpr{round((120.0*294 + 114.9*323)/617/2, 1)} (\Sexpr{round(sqrt((30^2*294 + 27.8^2*323)/617)/2, 1)})\footnote{Averages calculated assuming 294 males and 323 females.}
              & -- \\
Unscaled Scores & 44.0 (24.6)\footnote{Data from Part I only.}
                & 13.8 (4.5)
                & M:~120.0~(30.0), F:~114.9~(27.8)
                & --\\
{\footnotesize Population}    
              & \parbox[t]{.15\textwidth}{\footnotesize approx.\ 550 male\\ naval recruits} 
              & \parbox[t]{.15\textwidth}{\footnotesize 46 college students\\(1963~version)}
              & \parbox[t]{.3\textwidth}{\footnotesize suburban 11th \& 12th grade students\\(288-300 males, 317-329 females)}
              & \\\hline
\end{tabular}
